Investigation of results

### 2015-06-29 Articles/Presentation_ESEE_2015/Other results/Paul and Joao summary/Investigation.Rmd
Deleted, because this problem was operator error.

sum(resid(mod)^2)

@@

>>>>

EconModels:::sse(mod)

@@

```{r make model}
formulas <- 
  list( 
    PT = c(unadjusted = build_formula("iGDP", list("iKstkS.L", "iL", "iXpMP", "iYear")),
             adjusted = build_formula("iGDP", list("iKservS.L", "ihLest", "iUMP", "iYear"))),
    UK = c(unadjusted = build_formula("iGDP", list("iKstkO.WwithRD", "iL", "iXp", "iYear")),
             adjusted = build_formula("iGDP", list("iKservO.WwithRD", "ihLest", "iU", "iYear")))
  )
countries <- names(formulas)
flavors <- names(formulas$PT)

# Create the historicalData data frames
historicalData <- list()
commonVars <- c("Year", "Country", "Source")
historicalData$PT <- filter(IST, Country == "PT") 
historicalData$PT <- historicalData$PT[ , unique(c(commonVars,
                                                   all.vars(formulas$PT$unadjusted), 
                                                   all.vars(formulas$PT$adjusted)))]
historicalData$UK <- filter(Leeds, Country == "UK")
historicalData$UK <- historicalData$UK[ , unique(c(commonVars,
                                                   all.vars(formulas$UK$unadjusted), 
                                                   all.vars(formulas$UK$adjusted)))]

modMade <- cesModel(formulas$PT$adjusted, data=historicalData$PT, nest=c(3,1,2))
# Compare with model from models
rbind(naturalCoef(models$PT$adjusted$withE$CES$ekl), naturalCoef(modMade))
```
